### 2020-10-10 doc/manuscript/Dow_manuscript.Rmd
brief description of study sites / start of new discussion point

@@

>>>>

Our first study site was the forest dynamics plot located at the Smithsonian COnservation Biology Institute 5 KM South of Front Royal, Virginia within the Blue Ridge Mountains (38 °53036.6″ N, 78°08043.4″W; elevation 273–338 m). The forest here was established in the mid-19th century after conversion from agricultural fields. Dominate canopy species within the 25.6 HA forest plot include tulip poplar (Liriodendron tulipifera), hickories (Carya spp.), and oaks (Quercus spp.). The climate is humid temperate, with a mean annual precipitation of 998 mm, January temperatures averaging 1 degrees C and July temperatures averaging 24 degrees C (Helcoski et al, 2019).  
The second study site was Harvard Forest in the central Massachusetts town of Petersham (42°53′ N, 72°17′ W, elevation?). Harvard forest was established in 1907 as a study site for university students and researchers. (Previous use?) Dominate species within the approximately 13 HA plot are hemlock (Tsuga spp.), oak (Quercus spp.) and maple (Acer spp.). The climate is temperate continental with a mean annual precipitation of 1120 mm, January temperatures averaging -12 degrees C and July temperatures averaging 19 degrees C (D'Orangeville et al, ).

The third study site was the forest dynamics plot located at the Smithsonian Ecological Research Center in Edgewater, Maryland near a sub estuary of the Chesapeake Bay (38°88′ N, 76°55′ W, elevation?). The forest here established roughly 120 years ago, while the plot was established in 2007. The 16 HA plot is dominated by tulip poplar (Liriodendron tulipifera), oak (Quercus spp.), beech (Fagus spp.), hickory (Carya spp.), and maple (Acer spp.). (Climate summary)

@@

This analysis is one of a first generation of intraannual tree growth studies and as such, is the metaphorical tip of the ice berg. Here, we focused our analysis purely on early Spring warming. This falls short of the reality of our changing climate as every season if affected in some way. For example, diffuse porous trees seemed to show little, if any, relationship with the above climate window, but if we shift that window forward 20 days, the effect is much more severe, signalling a greater impact of May/June TMAX on trees of that wood type (figure or table?). A paper by Helcoski et al (2019) found that trees at SCBI had a significantly negative correlation between tree growth and May temperatures, agreeing with the results here. Other studies have found that Autumn leaf senescence  is being delayed, potentially in response to warmer temperatures in the previous year's Winter or Autumn (), this warming also impacts chilling requirements as well (), total growth is being stunted by drought and high TMAX in the current year's Summer (). How these realtionships may impact intraannual growth patterns or variables like thos described here is uncertain, but identifying such relationships will help us further understand how climate change is impacting our forests.

We present a mere stepping stone for future studies to build upon.
